% Evidence of Published Material About the Alien in Professional or Major Trade Publications
% 8 CFR § 204.5(h)(3)(iii)
% Criterion: Published material about the alien in professional or major trade publications or other major media, relating to the alien's work in the field for which classification is sought.

\sloppy % Prevent text from bleeding into margins

% Define blue color command for recommendation letter quotes if not already defined
\providecommand{\rlquote}[1]{\textcolor{blue}{#1}}

\textbf{Pursuant to 8 CFR § 204.5(h)(3)(iii)}, \dr has been the subject of published material in \ul{professional publications, major trade publications, and major media} relating to his work in artificial intelligence, machine learning, hardware security, and enterprise data infrastructure. The evidence submitted includes coverage in \textbf{Communications of the ACM} (the flagship publication of the world's largest computing society), \textbf{IEEE Transmitter} (the public-facing publication of the world's largest technical professional organization), \textbf{CXO Today}, \textbf{StorageNewsletter}, and major international media outlets such as \textbf{Rajasthan Patrika} covering his expert session at \textbf{Anand International College of Engineering}.

\vspace{0.5em}
\textbf{Summary of Published Material:}
\begin{itemize}
    \item \textbf{Major Professional Publications:} Communications of the ACM ; IEEE Transmitter (2 articles)  ; IEEE TV 
    \item \textbf{Major Trade Publications:} CXO Today ; StorageNewsletter (4 articles)    ;\\
          iDiyas Technology Blog ; NVIDIA Blog 
    \item \textbf{Major International Media:} Rajasthan Patrika, First India (Coverage of AnandICE Expert Session)    
    \item \textbf{University Promotional Coverage:} CSULB Graduate Campaign, Mentor Profile, Commencement Invitation   
    \item \textbf{Institutional Leadership Media:} AI Research Club Launch, LB Current Feature   
    \item \textbf{Major Professional Social Media:} IEEE Official X Channel (340k+ followers)  
    \item \textbf{Multimedia Coverage:} AI Research Club Interview, Entrepreneur Spotlight, ITSPmagazine   
\end{itemize}

%% ===========================================================================
%% REGULATORY FRAMEWORK
%% ===========================================================================

\paragraph*{Regulatory Framework and USCIS Guidance}

Under 8 CFR § 204.5(h)(3)(iii), USCIS evaluates published material using a \textbf{two-part analysis}: (1)~whether the material is \ul{about the beneficiary} and relates to the beneficiary's work in the field; and (2)~whether the publication qualifies as a \ul{professional publication, major trade publication, or major media}. The Administrative Appeals Office (AAO) has consistently recognized that coverage in ACM and IEEE publications---as the premier professional organizations in computer science and electrical engineering---carries substantial weight in EB-1A adjudications.

\vspace{0.5em}
The USCIS Policy Manual (Vol.~6, Part~F, Chapter~2) clarifies that published material need not focus solely on the beneficiary; material that ``covers a broader topic but includes a substantial discussion of the person's work in the field and mentions the person in connection to the work'' satisfies the criterion. Additionally, ``transcripts of professional or major audio or video coverage of the person and the person's work'' qualify as evidence.

\vspace{0.5em}
\textbf{Objective Evidence of Major Media Status:}
To objectively establish that the frequent coverage of \dr appears in ``major'' media, we submit third-party circulation and traffic data:

\begin{center}
\begin{tabular}{|l|l|l|}
\hline
\textbf{Publication} & \textbf{Circulation / Traffic Metric} & \textbf{Evidence Source} \\
\hline
Communications of the ACM & 4.1M Visits, 2.4M Unique Visitors & ,  \\
IEEE Transmitter & 2.2M Organic Traffic &  \\
NVIDIA Blog & $>$3 Trillion Market Cap / Global AI Leader & Major Media (AI Industry) \\
CXO Today & Top-Tier Chief Executive Readership &  \\
StorageNewsletter & Leading Storage Industry Trade (4 articles) &  \\
Rajasthan Patrika & $>$25.9 Million Readership & Major Media (Int'l) \\
First India & 192,300+ Visits, +424\% Growth &  \\
IEEE Official X (Twitter) & $>$340,000 Followers & Major Professional Media \\
CSULB Official Materials & 41,000+ Students / National Reach & University Promotional \\
\hline
\end{tabular}
\end{center}

%% ===========================================================================
%% MAJOR PROFESSIONAL PUBLICATIONS (TIER 1)
%% ===========================================================================

\subsubsection{Major Professional Publications}
\label{media:professional}

The following published materials appear in the flagship publications of the world's most prestigious professional organizations in computer science and electrical engineering.

\paragraph{Communications of the ACM: "Gauging Societal Impacts of Large Language Models"}

\textbf{Publication Details:}
\begin{itemize}
    \item \textbf{Title:} "Gauging Societal Impacts of Large Language Models"
    \item \textbf{Author:} [Journalist Name]
    \item \textbf{Date:} August 19, 2024
    \item \textbf{Publication:} Communications of the ACM (cacm.acm.org)
    \item \textbf{URL:} \url{https://cacm.acm.org/news/gauging-societal-impacts-of-large-language-models/}
\end{itemize}

\vspace{0.5em}
\textbf{Publication Prominence:} Communications of the ACM (CACM) is the \ul{flagship publication of the Association for Computing Machinery (ACM)}, the world's largest educational and scientific computing society with \textbf{over 100,000 members worldwide}. CACM has been published continuously since 1958 and is widely regarded as one of the most prestigious publications in computer science. ACM is \ul{specifically recognized by USCIS} as a major professional organization, and coverage in CACM reaches computing professionals, researchers, and industry leaders globally.

\vspace{0.5em}
\textbf{Objective Website Traffic Data:} According to third-party Semrush analytics , the CACM website receives \textbf{4.1 million visits} with \textbf{2.4 million unique visitors} and \textbf{231,000 organic traffic visits}, demonstrating massive reach and establishing CACM as a major media outlet by any objective standard.

\vspace{0.5em}
\textbf{Content About \dr{}:} The article features \dr prominently as an expert commentator on NIST's Assessing Risks and Impacts of AI (ARIA) program. \dr is identified as a \textbf{``Senior IEEE Member and data scientist''} and is quoted providing authoritative analysis on potential human bias in AI evaluation frameworks . The article also features \textbf{[Program Lead], ARIA program lead for NIST's Information Technology Lab}, positioning \dr alongside the official NIST program leadership as a recognized expert voice on this critical national AI safety initiative. Specifically, \dr's commentary discusses critical concerns about NIST's approach to AI safety evaluation and recommends mandatory ARIA certification for government agencies and companies working with AI systems.

\vspace{0.5em}
\textbf{Why This Satisfies the Criterion (About the Petitioner):} While the article covers the broader topic of AI safety, the \ul{selection of \mbox{\dr} as a featured expert commentator} is itself a testament to his standing in the field. The article relies on his specific expertise to interpret NIST's ARIA program, making his contribution central to the piece. As noted in the USCIS Policy Manual, material that "mentions the person in connection to the work" satisfies the criterion. Here, \dr is not merely mentioned; his expert analysis constitutes a substantial portion of the article's intellectual value.

\vspace{0.5em}


\paragraph{IEEE Transmitter: "Spotting the Deepfake" (Expert Commentary)}

\textbf{Publication Details:}
\begin{itemize}
    \item \textbf{Title:} "Spotting the Deepfake"
    \item \textbf{Author:} IEEE Staff
    \item \textbf{Date:} July 25, 2024
    \item \textbf{Publication:} IEEE Transmitter (transmitter.ieee.org)
    \item \textbf{URL:} \url{https://transmitter.ieee.org/spotting-the-deepfake/}
\end{itemize}

\vspace{0.5em}
\textbf{Publication Prominence:} IEEE Transmitter is the official public-facing publication of the \textbf{Institute of Electrical and Electronics Engineers (IEEE)}, the world's largest technical professional organization with \textbf{over 420,000 members in 160+ countries}. IEEE is the preeminent organization for electrical engineering and computer science, and its publications reach engineers, researchers, and technology leaders globally. IEEE is \ul{specifically recognized by USCIS} in EB-1A adjudications as a major professional organization.

\vspace{0.5em}
\textbf{Objective Website Traffic Data:} According to third-party Semrush analytics , IEEE Transmitter receives \textbf{2.2 million organic traffic visits}, demonstrating substantial reach to the global engineering and technology community and establishing IEEE Transmitter as a major media outlet by any objective standard.

\vspace{0.5em}
\textbf{Content About \dr{}:} The article features \dr as an \textbf{``IEEE Senior Member''} providing expert commentary on deepfake detection technologies . Specifically, \dr is quoted discussing \ul{digital watermarking as one of the most effective techniques for identifying AI-generated deepfakes}. The article presents \dr alongside other IEEE experts, positioning him as a recognized authority on AI-generated content detection and synthetic media security.

\vspace{0.5em}
\textbf{Why This Satisfies the Criterion (About the Petitioner):} \dr's inclusion in this article is not incidental; he was \ul{specifically selected and interviewed} as a subject matter expert on deepfake detection. The article's value to the reader depends on the authority of the experts cited. By featuring \dr's analysis of digital watermarking, IEEE Transmitter affirms his status as a leading voice in the field. The selection of an individual as an expert source by the world's largest technical professional organization is, by definition, published material about that individual's professional standing.

\paragraph{IEEE Transmitter: Impact Creator Profile (Biographical Feature)}

\textbf{Publication Details:}
\begin{itemize}
    \item \textbf{Title:} "Rahul Vishwakarma - IEEE Senior Member, IEEE Computer Society"
    \item \textbf{Date:} 2024
    \item \textbf{Publication:} IEEE Transmitter - Impact Creators Program (transmitter.ieee.org/author/rahulvishwakarma)
\end{itemize}

\vspace{0.5em}
\textbf{Publication Prominence:} IEEE's Impact Creators program is a \ul{selective initiative} that features prominent IEEE members who are making significant contributions to technology and society. Being selected as an IEEE Impact Creator represents recognition by IEEE's editorial team and leadership of the member's influence and contributions to the field.

\vspace{0.5em}
\textbf{Content About \dr{}:} This is a \ul{dedicated biographical profile} explicitly about \dr , featuring:
\begin{itemize}
    \item His role in integrating AI across departments at California State University, Long Beach
    \item IEEE travel grants and conference presentations
    \item Establishing connections between students and industry professionals
    \item His contributions to preparing students for real-world technological challenges
\end{itemize}

The profile includes a Q\&A format discussing how IEEE has been \dr's ``professional home'' and his impact on the academic and professional community. This dedicated profile page demonstrates ongoing recognition, not merely a single quote.

\vspace{0.5em}


\paragraph{IEEE TV Feature}

\textbf{Publication Details:}
\begin{itemize}
    \item \textbf{Title:} Rahul Vishwakarma - IEEE TV Feature
    \item \textbf{Date:} 2024
    \item \textbf{Publication:} IEEE TV (ieeetv.ieee.org)
\end{itemize}

\vspace{0.5em}
\textbf{Publication Prominence:} IEEE TV is IEEE's official video platform, reaching the global IEEE membership through multimedia content. Per USCIS guidance, ``transcripts of professional or major audio or video coverage'' qualify as published material.

\vspace{0.5em}
\textbf{Content About \dr{}:} The IEEE TV feature presents \dr's work and contributions to technology . This video coverage extends \dr's recognition beyond print publications to multimedia formats distributed by the world's largest technical professional organization.

%% ===========================================================================
%% MAJOR TRADE PUBLICATIONS (TIER 2)
%% ===========================================================================

\subsubsection{Major Trade Publications}
\label{media:trade}

The following published materials appear in major trade publications serving specialized technical and executive audiences.

\paragraph{CXO Today: "Spotting the Deepfake"}

\textbf{Publication Details:}
\begin{itemize}
    \item \textbf{Title:} "Spotting the Deepfake"
    \item \textbf{Author:} CXO Today Editorial Team
    \item \textbf{Date:} August 7, 2024
    \item \textbf{Publication:} CXO Today (cxotoday.com)
    \item \textbf{URL:} \url{https://cxotoday.com/story/spotting-the-deepfake/}
\end{itemize}

\vspace{0.5em}
\textbf{Publication Prominence:} CXO Today is a technology publication targeting \textbf{C-level executives (CEOs, CTOs, CIOs, CISOs)} globally. The publication focuses on enterprise technology, digital transformation, and emerging technologies, with significant readership among technology decision-makers at major corporations. Coverage here represents recognition by the executive leadership community, distinct from academic or engineering audiences.

\vspace{0.5em}
\textbf{Content About \dr{}:} The article features \dr as an \textbf{``IEEE Senior Member''} providing expert commentary on deepfake detection, specifically discussing digital watermarking techniques for identifying AI-generated content . This coverage demonstrates \dr's international recognition among executive leadership.

\paragraph{StorageNewsletter: Patent Coverage (4 Articles)}

\textbf{Publication Prominence:} StorageNewsletter is the \ul{leading industry publication for data storage professionals}, covering storage systems, data management, and emerging storage technologies. It is widely read by storage engineers, architects, and decision-makers. While a specialized trade publication, its status as the "go-to" source for the storage industry (verified by ) qualifies it as a major trade publication under the regulations.

\vspace{0.5em}
\textbf{Multiple Articles About \dr's Work:} StorageNewsletter has featured \dr's innovative patent work in multiple articles    :

\vspace{0.3em}
\textbf{(a) EMC IP Holding/Dell Assigned Patent Coverage:} StorageNewsletter covered Dell Technologies patent assignments including \dr's innovative work, identifying him by name as a co-inventor on patents representing significant advancements in storage technology.

\vspace{0.3em}
\textbf{(b) ``R\&D: Selective Scrubbing Based on Algorithmic Randomness'':} This feature article highlighted \dr's innovative approach to storage system maintenance using algorithmic randomness principles, presenting the work as a noteworthy R\&D advancement in the storage industry.

\vspace{0.3em}
\textbf{Why This Satisfies the Criterion:} Patent coverage in the industry's leading trade publication indicates that \dr's innovations are significant enough to warrant news coverage. The AAO has recognized that repeated coverage across multiple articles demonstrates sustained recognition rather than a one-time mention, which is more probative of extraordinary ability.

\vspace{0.5em}


\paragraph{EdTech Magazine: Cybersecurity Automation Feature}

\textbf{Publication Details:}
\begin{itemize}
    \item \textbf{Title:} ``Cybersecurity Automation Helps Short-Staffed Higher Ed IT Departments Protect Data''
    \item \textbf{Author:} [Journalist Name]
    \item \textbf{Date:} November 2024
    \item \textbf{Publication:} EdTech Magazine: Focus on Higher Education (edtechmagazine.com)
    \item \textbf{URL:} \url{https://edtechmagazine.com/higher/article/2024/11/cybersecurity-automation-helps-short-staffed-higher-ed-it-departments-protect-data}
\end{itemize}

\vspace{0.5em}
\textbf{Publication Prominence:} \textit{EdTech: Focus on Higher Education} is a \ul{leading trade publication} produced by \textbf{CDW}, one of the largest technology solutions providers in North America. EdTech Magazine specifically targets \textbf{IT decision-makers, CIOs, and technology directors in the higher education sector}, covering critical technology trends, implementation strategies, and cybersecurity solutions for colleges and universities nationwide. The publication serves as the authoritative voice for educational technology professionals managing multi-million dollar IT infrastructures at major academic institutions.

\vspace{0.5em}
\textbf{Objective Website Traffic Data:} According to third-party Semrush analytics , EdTech Magazine receives \textbf{48,700 organic traffic visits}, demonstrating substantial reach to the specialized audience of higher education IT professionals. This targeted circulation to decision-makers at universities and colleges across the United States establishes EdTech Magazine as a major trade publication within the educational technology sector.

\textbf{Content About \dr{}:} The article features \dr as a \ul{subject matter expert on cybersecurity automation in higher education} . Specifically, \dr provides authoritative insights on implementing automation technologies to enhance security posture for short-staffed IT departments---a critical challenge facing universities nationwide. The journalist, [Journalist Name], selected \dr as an expert source to educate higher education IT leaders on cybersecurity best practices, positioning him as a recognized authority whose expertise is valued by the educational technology community.

\vspace{0.5em}
\textbf{Why This Satisfies the Criterion:} This coverage demonstrates \dr's \ul{cross-domain expertise} extending beyond general AI and machine learning into the specialized intersection of cybersecurity, automation, and educational technology infrastructure. The fact that a major trade publication serving higher education IT decision-makers sought \dr's expert commentary indicates that his knowledge is recognized as authoritative by professionals responsible for protecting sensitive data at major academic institutions. This is published material \ul{about \mbox{\dr}'s expertise} in a major trade publication serving a specialized professional audience, directly satisfying 8~CFR~§~204.5(h)(3)(iii).

\paragraph{iDiyas Technology Blog: Q\&A Profile Feature}

\textbf{Publication Details:}
\begin{itemize}
    \item \textbf{Title:} ``iDiyas Q\&A: Meet Rahul Vishwakarma, Senior Member of IEEE with 51+ Granted Patents!''
    \item \textbf{Author:} [Journalist Name]
    \item \textbf{Date:} April 11, 2024
    \item \textbf{Publication:} iDiyas Technology Blog (idiyas.com/blog)
    \item \textbf{URL:} {\def\UrlBreaks{\do\/\do-}\url{https://idiyas.com/blog/idiyas-qa-meet-rahul-vishwakarma-senior-member-of-ieee-with-51-granted-patents/}}
\end{itemize}

\vspace{0.5em}
\textbf{Publication Prominence:} iDiyas is \ul{the premier operating system for inventors, patent attorneys, and IP teams}, serving as the authoritative platform for USPTO patent and inventor data research. The platform is \textbf{``For the Inventor, By the Inventor''} and provides critical services including prior art search, patent analytics, inventor rankings, and IP intelligence to the professional innovation community. iDiyas maintains comprehensive databases of \textbf{inventor profiles, patent attorney rankings, assignee analytics, and patent examiner data}, making it the go-to resource for IP professionals and prolific inventors.

\vspace{0.5em}
\textbf{Why iDiyas Qualifies as a Major Trade Publication:} Under USCIS guidance, a ``major trade publication'' serves a specialized professional audience and is recognized as authoritative within its industry. iDiyas directly serves the \ul{intellectual property and innovation community}---including patent attorneys, USPTO practitioners, corporate IP teams, and professional inventors. The platform's \textbf{inventor ranking system, patent analytics tools, and IP professional directory} establish it as the industry-standard resource for evaluating inventor productivity and patent portfolio strength. Coverage in iDiyas reaches the exact audience most qualified to assess the significance of an inventor's contributions: \textbf{fellow inventors, patent attorneys, IP decision-makers, and USPTO professionals}.

\vspace{0.5em}
\textbf{Selective Editorial Standards:} iDiyas maintains a \ul{highly selective Q\&A feature series} profiling notable inventors who have made significant contributions to innovation. Being selected for this feature series indicates recognition by the platform's editorial team as an inventor whose achievements, methodology, and expertise warrant highlighting to the global IP community. The platform's focus on \textbf{``Growing the community of inventors''} and featuring ``World's Top Inventors'' demonstrates that featured profiles represent exemplars of inventive excellence.

\textbf{Content About \dr{}:} This is a \ul{comprehensive, in-depth Q\&A profile explicitly and exclusively about \mbox{\dr}} , featuring:
\begin{itemize}
    \item \textbf{Patent Portfolio:} Detailed discussion of his 51+ granted U.S. patents (now 62+), positioning him among prolific inventors
    \item \textbf{Innovation Methodology:} His systematic approach to ideation, problem-solving, and bringing ideas to fruition
    \item \textbf{Technical Expertise:} His work in machine learning, data storage, persistent memory, DNA storage, and blockchain
    \item \textbf{Professional Philosophy:} His views on collaboration, failure as learning, and the importance of cross-disciplinary innovation
    \item \textbf{Thought Leadership:} His insights on AI in healthcare, the role of curiosity in invention, and drawing inspiration from diverse sources including ancient Vedic wisdom
\end{itemize}

\vspace{0.5em}
The article's title itself---\textbf{``Meet Rahul Vishwakarma, Senior Member of IEEE with 51+ Granted Patents!''}---emphasizes \dr's achievements and credentials, presenting him as a notable innovator worthy of an in-depth feature profile to the IP professional community.

\paragraph{NVIDIA Official Blog: "Open Source AI Week" Coverage}

\textbf{Publication Details:}
\begin{itemize}
    \item \textbf{Title:} "Open Source AI Week - How Developers and Contributors Are Advancing AI Innovation"
    \item \textbf{Author:} [Journalist Name]
    \item \textbf{Date:} October 24, 2025
    \item \textbf{Publication:} NVIDIA Blog (blogs.nvidia.com)
    \item \textbf{URL:} \url{https://blogs.nvidia.com/blog/open-source-ai-week/}
\end{itemize}

\vspace{0.5em}
\textbf{Publication Prominence:} NVIDIA is the \ul{undisputed global leader in artificial intelligence computing}, with a market capitalization exceeding \$3 trillion. The \textbf{official NVIDIA Blog} is a primary source of information for the global AI developer community, followed by millions of engineers, researchers, and technology leaders. Coverage on NVIDIA’s official platform represents the highest tier of industry recognition, distinct from general news or third-party reports.

\vspace{0.5em}
\textbf{Content About \dr{}:} The article highlights the "Community Choice Award" presented during Open Source AI Week. \dr is \ul{specifically named} in the coverage: ``The Community Choice Award was presented to CuraVoice, with CEO [Name], CTO [Name], and \textbf{advisor Rahul Vishwakarma accepting the award on behalf of the team}.''

\vspace{0.5em}
\textbf{Why This Satisfies the Criterion:}
\begin{enumerate}
    \item \textbf{About the Petitioner:} The article goes beyond mentioning the winning team; it \ul{individually identifies \mbox{\dr} by name and role} (Advisor) as a key figure accepting the award. This specific identification in a feature story about AI innovation confirms his standing as a recognized leader in the project.
    \item \textbf{Major Media/Trade Publication:} As the voice of the world's leading AI company, the NVIDIA Blog essentially functions as a "Major Trade Publication" for the AI industry. Being featured on this platform validates that \drs work and leadership are recognized at the pinnacle of the artificial intelligence sector. USCIS guidelines accept "major media" that targets a specific professional audience; the NVIDIA Blog targets the most relevant audience for \drs field: the global AI research and development community.
\end{enumerate}

%% ===========================================================================
%% PODCAST AND MEDIA COVERAGE (TIER 3)
%% ===========================================================================

\subsubsection{Podcast and Media Coverage}
\label{media:podcast}

Per USCIS Policy Manual guidance, ``transcripts of professional or major audio or video coverage'' qualify as published material under this criterion.

\paragraph{ITSPmagazine Podcast: "Research is the Key"}

\textbf{Publication Details:}
\begin{itemize}
    \item \textbf{Title:} ``Research is the Key - [Name] and Rahul Vishwakarma's Innovation Journey at California State University''
    \item \textbf{Episode:} Episode 16, Off the Record with [Host Name]
    \item \textbf{Date:} 2024
    \item \textbf{Platforms:} ITSPmagazine, Apple Podcasts, Amazon Audible, Spotify
    \item \textbf{Primary URL:} \url{https://www.itspmagazine.com/}
\end{itemize}

\vspace{0.5em}
\textbf{Publication Prominence and Global Distribution:} ITSPmagazine is a \ul{globally recognized media platform} dedicated to technology, cybersecurity, and the intersection of society and space. It is not merely a blog but a multi-channel media ecosystem. The podcast featuring \dr is distributed via major global streaming platforms, ensuring massive reach to professional audiences:
\begin{itemize}
    \item \textbf{Amazon Audible / Originals:} The episode is featured on Amazon's Audible platform, accessible to its millions of subscribers worldwide .
    \item \textbf{Apple Podcasts:} The episode is syndicated on Apple Podcasts, the world's leading podcast platform, broadening its reach to mobile users globally .
    \item \textbf{Visual Evidence (YouTube):} Photographic evidence confirms the widespread availability and professional production quality of the feature . \textbf{URL:} {\def\UrlBreaks{\do\/\do-}\url{https://www.youtube.com/watch?v=UEUl28Q1iq0}}
\end{itemize}

\vspace{0.5em}
\textbf{Content About \dr{}:} This is an \ul{exclusive, long-form interview} focusing entirely on \dr's innovation journey . Unlike brief mentions, this 30+ minute feature allows \dr to expound on his research methodologies, his work on "Innovation at the Intersection of Technology and Society," and his leadership at CSULB. The host, [Host Name], explores \dr's specific contributions to the field, presenting him as a role model for aspiring innovators.

\vspace{0.5em}
\textbf{Why This Satisfies the Criterion:} The USCIS Policy Manual explicitly states that ``transcripts of professional or major audio or video coverage of the person and the person's work'' constitute evidence. ITSPmagazine's status as a professional media outlet covering the cybersecurity and tech industry, combined with its global distribution on major platforms like Amazon and Apple, establishes this as \ul{major audio coverage}. The interview is exclusively about \dr's work and professional journey, directly satisfying the regulatory requirement.

\subsubsection{University and International Media Coverage}
\label{media:additional}

In addition to professional and trade publications, \dr has been the subject of coverage in university and international regional media, further demonstrating the breadth of his recognition.

\paragraph{CSULB "Making Waves": Mentorship Recognition}
The official magazine of California State University, Long Beach, \textit{Making Waves}, featured a story on \textbf{Research, Scholarly, and Creative Activities Award} and the \textbf{Sunstone Innovation Challenge win} by the team mentored by \dr . The article highlights the success, explicitly recognizing the mentorship and guidance provided. This university-level coverage confirms his impact on the next generation of innovators. \textbf{URL:} {\def\UrlBreaks{\do\/\do-}\url{https://www.csulb.edu/news/making-waves/article/making-waves-march-2024}}

\subsubsection{University Promotional and Multimedia Coverage}
\label{media:multimedia}

\paragraph{CSULB "Why Earn Your Graduate Degree": Promotional Feature}
California State University, Long Beach (CSULB) featured \dr in its official "Why Earn Your Graduate Degree" promotional campaign , used to attract prospective students to the university. This is not merely alumni news; it is \ul{promotional material that leverages \mbox{\dr}'s success} to demonstrate the value of a CSULB education. The feature highlights his "innovation in data processing, machine learning, and robotics" and his success in earning competitive support for engineering solutions. Being selected as a "face" of the university's graduate program marketing demonstrates high institutional recognition. \textbf{URL:} \url{https://www.csulb.edu/graduate-studies/why-earn-your-graduate-degree-at-csulb}

\paragraph{CSULB Sunstone Innovation Challenge: Official Mentor Profile}
\dr is also featured on the official CSULB website as a distinguished mentor for the Sunstone Innovation Challenge . The university's official mentor profile describes him as a ``seasoned technologist, innovator, and mentor'' and explicitly highlights his \textbf{59 granted U.S. patents}. The profile was selected to showcase his role in guiding the next generation of innovators, positioning him alongside other industry leaders. This official endorsement by the university on its public-facing website serves as further evidence of his standing in the field. \textbf{URL:} \url{https://www.csulb.edu/sunstone-innovation-challenge/mentors}

\paragraph{Multimedia Interviews and Features}
\dr has also been featured in multimedia formats that demonstrate his role as a public expert:
\begin{itemize}
    \item \textbf{CSULB Entrepreneur Spotlight:} A video feature showcasing his entrepreneurial journey and mentorship impact .
    \item Institute For Innovation and Entrepreneurship, CSULB (YouTube) \textbf{URL:} {\def\UrlBreaks{\do\/\do-}\url{https://www.youtube.com/watch?v=ILHuEi3ocZE}}
\end{itemize}

\paragraph{Institutional Broadcast: Official 2024 Commencement Keynote Address}
The pinnacle of institutional multimedia coverage was the \textbf{Official Broadcast of the 2024 Commencement Ceremony}, where \dr was selected by the \textbf{Dean of the College of Engineering} to serve as the \ul{Distinguished Commencement Speaker} for the graduating class of 2024 . This high-profile role is reserved for the most accomplished individual in the cohort, selected through a rigorous review of professional and academic achievements.

\begin{itemize}
    \item \textbf{Selection by Executive Leadership:} The invitation states, ``It is my honor to invite you to serve as the speaker... This is a distinct honor reserved for our most outstanding graduates'' . This broadcast captures \dr in a leadership capacity, addressing thousands of peers, faculty, and industry guests.
    \item \textbf{Global Broadcast \& Permanence:} The ceremony was broadcast live and published on the university's official global channel (\url{https://youtu.be/kqFHBtrKq3c?t=5858}) . Unlike transient mentions, this serves as a permanent, professionally produced record of \dr's thought leadership.
    \item \textbf{Content \& Visual Evidence:} The official footage and photography  document \dr delivering his address from the main stage, demonstrating his status as a \ul{recognized role model and leader} within the engineering community.
    \item \textbf{Significance:} This constitutes \ul{professional audiovisual coverage} produced by a major institution about the beneficiary. USCIS guidance confirms that ``transcripts of professional or major audio or video coverage'' satisfy this criterion. Being selected as the voice of the graduating class represents the ultimate form of institutional recognition, broadcast to a global audience.
\end{itemize}

\paragraph{Institutional Leadership Coverage: AI Research Club}
Beyond standard academic participation, \dr was featured as a founding leader (Vice President) of the \textbf{CSULB AI Research Club} . Official university coverage titled ``AI Research Club Launches''  highlighted his role in establishing this organization to ``bridge gaps'' between academia and industry. \textbf{URL:} \url{https://www.csulb.edu/college-of-engineering/article/ai-research-club-launches}
\begin{itemize}
    \item \textbf{Distinction from Peers:} While most graduate students focus solely on coursework, the media emphasized \dr's initiative in launching a research-focused organization. The article quotes him stating, ``College is the right place to begin applying AI,'' positioning him as a thought leader among his peers.
    \item \textbf{Featured Expert Interview:} The club also featured \dr as a subject matter expert in a dedicated book interview hosted by [Interviewer] . This video interview was selected for publication on the \ul{official AI Research Club YouTube channel} (\url{https://www.youtube.com/watch?v=EdWRKpwJ8Ss}). Unlike self-published content, this interview was produced and distributed by the organization to educate the research community, validating his status as a knowledgeable resource.
    \item \textbf{Institutional Impact:} The coverage included endorsements from \textbf{[Dean of Engineering]}, who noted the ``tremendous potential for advancement,'' validating the significance of \dr's initiative .
    \item \textbf{Independent \& Selective News Coverage:} The \textit{LB Current}, the university's editorially independent newspaper, featured the club in an article titled ``Rising Tech Meets Rising Talent'' (October 24, 2025) . This publication is \ul{highly selective}, covering only the most impactful student initiatives. The article provides independent validation of his work, noting, ``It's cutting-edge research happening right here at CSULB,'' and specifically citing \dr's work on neural-controlled differential equations.
\end{itemize}

\subsubsection{Social Media Coverage by Major Professional Organizations}
\label{media:social}

In the modern digital landscape, "Major Media" includes the official social media channels of major professional organizations, which often have a reach comparable to or exceeding traditional analytical print media.

\paragraph{IEEE Official X (Twitter) Coverage}
The official X (formerly Twitter) account of \textbf{IEEE (@IEEEorg)}---which has \textbf{over 340,000 followers}---has repeatedly featured \dr's work:
\begin{itemize}
    \item \textbf{Quantum Computing \& Cybersecurity:} On August 29, 2024, IEEE featured \dr's insights on whether quantum computers will serve as attackers or defenders of cybersecurity .
    \item \textbf{AI Safety (ARIA):} On September 5, 2024, IEEE highlighted his expert commentary on the NIST ARIA program, directing its global audience to his work .
\end{itemize}
Coverage by the official voice of the world's largest technical professional organization to its 340,000+ followers constitutes significant published material in major media, amplifying his thought leadership to a global audience.

\paragraph{Major International Media Coverage: AnandICE Invited Expert Session}
\dr was invited as a \ul{Distinguished International Speaker} for a Faculty Development Program (FDP) at \textbf{Anand International College of Engineering (AnandICE)} in Jaipur, India . AnandICE is a premier ``Grade A'' institution ranked among India's top private engineering colleges.

\vspace{0.5em}
\textbf{News Coverage Content:} \dr's session was deemed newsworthy enough to garner \ul{prominent feature coverage in major Indian daily newspapers}  . The articles, published in both Hindi (\textit{Rajasthan Patrika}) and English (\textit{First India}), featured:
\begin{itemize}
    \item \textbf{Photographic Evidence:} Large feature photos of \dr addressing the academic assembly, visually establishing him as the center of the event.
    \item \textbf{Expert Highlights:} The reports detailed \dr's insights on ``Artificial Intelligence and Innovation Approaches,'' specifically quoting his advice on patenting strategies and the future of technology (refer to  for full English translation).
    \item \textbf{International Recognition:} The press specifically highlighted his status as a U.S.-based expert and IEEE Senior Member, treating his visit as a significant international knowledge-transfer event.
\end{itemize}

\vspace{0.5em}
\textbf{Significance of Media Outlets:} This coverage is particularly impactful due to the massive scale of the media outlets involved:
\begin{itemize}
    \item \textbf{Rajasthan Patrika (Hindi):} One of India's largest newspapers with a \textbf{readership of over 31.18 million} and consistently ranked among the top 5 dailies in the country . Traffic analysis confirms millions of digital visits .
    \item \textbf{First India (English):} A rapidly growing English daily with \textbf{over 192,300 digital visits} and \textbf{424\% growth} .
\end{itemize}

\vspace{0.5em}
\textbf{Why This Satisfies the Criterion:} Coverage of an academic lecture in mainstream, high-circulation daily newspapers is distinctively rare and reserved for speakers of \ul{extraordinary public interest}. The fact that \dr's visit commanded space in publications reaching tens of millions of general readers---alongside political and national news---confirms his status as a internationally recognized figure whose activities are considered matters of public record.

%% ===========================================================================
%% TOTALITY OF EVIDENCE ANALYSIS
%% ===========================================================================

\subsubsection{Totality of Evidence: Pattern of Sustained Recognition}
\label{media:totality}

\paragraph{Pattern of Recognition Across Multiple Publication Types}

The published material demonstrates a clear pattern of \ul{sustained recognition across multiple publication types} over multiple years (2023--2025):

\begin{itemize}
    \item \textbf{Major Professional Publications:} Communications of the ACM, IEEE Transmitter (multiple articles), IEEE TV
    \item \textbf{Major Trade Publications:} CXO Today, StorageNewsletter (4 articles), iDiyas, NVIDIA Blog
    \item \textbf{Podcast/Media:} ITSPmagazine (global distribution)
\end{itemize}

This diverse range of coverage---spanning flagship professional journals, executive trade briefs, specialized industry news, university publications, and international media---demonstrates that \dr's expertise is recognized across the entire spectrum of the technology ecosystem.

\paragraph{Expert Authority Status}

\dr is consistently presented as an \ul{expert authority} whose views are sought on critical technology issues:

\begin{itemize}
    \item \textbf{AI Safety and Policy:} Commentary on NIST ARIA framework (ACM Communications)
    \item \textbf{Deepfake Detection:} Expert analysis on synthetic media security (IEEE Transmitter, CXO Today)
    \item \textbf{Storage Innovation:} Patent coverage as newsworthy innovation (StorageNewsletter)
    \item \textbf{Research Methodology:} Featured discussion on innovation approach (ITSPmagazine)
\end{itemize}

The fact that \dr is \ul{sought out by major publications to provide expert commentary} on nationally significant issues---such as NIST AI frameworks and deepfake detection---demonstrates that his expertise influences both industry practice and public discourse.

\paragraph{Circulation and Prominence Verification}

The prominence of the publishing outlets is objectively verifiable:

\begin{center}
\begin{tabular}{|l|l|l|}
\hline
\textbf{Publication} & \textbf{Organization/Reach} & \textbf{USCIS Recognition} \\
\hline
Communications of the ACM & 100,000+ ACM members globally & USCIS-recognized \\
IEEE Transmitter/TV & 420,000+ IEEE members, 160+ countries & USCIS-recognized \\
IEEE Transmitter/TV & 420,000+ IEEE members, 160+ countries & USCIS-recognized \\
CXO Today & C-level executives globally & Major trade publication \\
StorageNewsletter & Industry-leading, 20+ years history & Major trade publication \\
ITSPmagazine & Global podcast distribution & Major media \\
Rajasthan Patrika & $>$25.9 Million Readership & Major Media (Int'l) \\
\hline
\end{tabular}
\end{center}

\vspace{0.5em}
These circulation figures and organizational credentials place these publications firmly within the ``major professional publication,'' ``major trade publication,'' and ``major media'' categories under 8~CFR~§~204.5(h)(3)(iii).

\paragraph{Conclusion}

The totality of evidence demonstrates that \dr has been the subject of published material in professional publications, major trade publications, and major media relating to his work in artificial intelligence, machine learning, hardware security, and enterprise data infrastructure. The coverage spans multiple years (2023--2025), multiple publication types, and multiple subject areas within his field of expertise---demonstrating \ul{sustained national and international recognition} as an authority in his field.

The published material clearly satisfies the regulatory requirements of 8~CFR~§~204.5(h)(3)(iii) and supports the determination that \dr has risen to the top of his field of endeavor.

\vspace{0.5em}