%% ===========================================================================
%% STATEMENT OF INTENT TO CONTINUE WORK IN THE UNITED STATES
%% ===========================================================================

\textbf{Pursuant to 8 CFR ยง 204.5(h)(5)}, I, \textbf{Rahul Deo Vishwakarma}, hereby declare my clear and firm intent to continue working in my field of extraordinary ability---Artificial Intelligence and Machine Learning in Enterprise Data Infrastructure and Security---upon approval of this petition.

My continued work in the United States will focus on advancing critical national priorities in AI Safety, Hardware Security, and Secure Enterprise Infrastructure, directly aligning with the strategic objectives of the CHIPS and Science Act of 2022 and Executive Order 14110 (Safe, Secure, and Trustworthy AI).

\subsection*{Plan for Continued Work}

My future work in the United States will proceed along three parallel and mutually reinforcing tracks:

\paragraph{Advancing AI Safety and Reliability in Enterprise Systems}
As Research Engineer at WorkOnward, I will continue to lead the development of Generative AI-based workforce solutions. My primary focus is on implementing Uncertainty Quantification (UQ) and Conformal Prediction frameworks to ensure that AI systems deployed in high-stakes enterprise environments are reliable, explainable, and safe. This directly addresses the mandate of Executive Order 14110 to develop "standards, tools, and tests to help ensure that AI systems are safe, secure, and trustworthy." I intend to expand my portfolio of 62 U.S. patents by developing new intellectual property that solves the "black box" problem in industrial AI.

\paragraph{Strengthening Critical Infrastructure via Hardware Security Research}
Beuilding on my NSF-funded research (Grant \#2245247 and \#2131156), I intend to continue my investigations into Hardware Trojan Detection and Post-Quantum Cryptography for edge devices. By developing multimodal deep learning frameworks (like my NOODLE and PALETTE systems) to detect malicious modifications in semiconductor supply chains, my work will directly support the CHIPS and Science Act's goal of securing the U.S. defense industrial base against supply chain attacks. I plan to publish these findings in premier venues (IEEE/ACM) and release open-source tools to arm the U.S. security community against emerging threats.

\paragraph{Mentoring the Next Generation of U.S. Innovators}
I am committed to continuing my role as a Mentor at the California State University, Long Beach (CSULB) Institute for Innovation \& Entrepreneurship. By guiding diverse student teams in applying AI to real-world problems (as demonstrated by my mentorship of the award-winning "CuraVoice" team), I will help cultivate a skilled STEM workforce. This supports the National Strategy for STEM Education by ensuring that the U.S. retains its competitive edge in technology talent.

\vspace{1em}
\subsection*{National Interest Alignment}

My intended work is prospectively beneficial to the United States because it:
\begin{itemize}
    \item Secures Critical Supply Chains: My hardware security research protects the semiconductor chips that power U.S. defense and economic systems.
    \item Enhances Economic Competitiveness: My patent portfolio in enterprise data infrastructure (cited by Amazon, Google, Dell) drives efficiency in the cloud computing sector, a cornerstone of the U.S. economy.
    \item Promotes AI Leadership: My work on "safe AI" frameworks ensures that the United States remains the global leader in responsible AI deployment, countering influence from strategic competitors.
\end{itemize}

I hereby certify that I will continue to work in this area of extraordinary ability and that my presence in the United States will provide a substantial benefit to the nation.

\vspace{4em}

Sincerely,

\vspace{3em}

\rule{0.5\textwidth}{0.4pt} \\
\textbf{Rahul Deo Vishwakarma} \\
Petitioner (Self-Petitioner) \\ \relax
[Street Address, City, State, ZIP] \\ \relax
[Phone Number] \\ \relax
[Email Address] \\
Date: \today
